% Document class and font size
\documentclass[a4paper,10pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Begin document
\begin{document}


% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
	\textbf{\Large ALY TARFA}\\[2pt]
	Ottawa, Ontario | \href{mailto:alytarfa@gmail.com}{alytarfa@gmail.com} | (647) 972-2444 | \href{https://www.linkedin.com/in/aly-tarfa-b18b59225/}{Linkedin} | \href{https://alytarfa.me/}{alytarfa.me}
\end{center}

% Education Section
\section*{EDUCATION}
\noindent
\textbf{Carleton University}, Ottawa, Ontario \hfill September 2022 | June 2027\\
Bachelor of Computer Science: Software Engineering Stream, CO-OP \hfill Second Year Standing\\
Available for 4 months beginning April 2023 \hfill CGPA: 11.10 (A)

% Projects Section
\section*{APPLIED PROJECTS}
\noindent
\textbf{ASCII Art Web App} \hfill November 2023 - Ongoing\\
\url{https://github.com/xQuilled/ascii-art-app} \hfill node.js, SQLite, express, CSS, HTML, Javascript
\begin{itemize}
	\item Integrated an external API to enable users to generate text-based ASCII art, adding a unique feature to the website.
	\item Created a reliable database with SQLite3 that enhances the overall performance and security of the website, ensuring smooth user interactions and data integrity.
	\item Implemented user authentication and authorization, allowing users to register and login with a username and password.
	\item Designed a responsive and intuitive user interface, resulting in a seamless user experience.
\end{itemize}


\noindent
\textbf{Within Yourself | 3D Video Game} \hfill December 2021 - January 2022\\
\url{https://quilled.itch.io/within-yourself} \hfill Godot Engine, Blender, GDScript, Audacity
\begin{itemize}
	\item Successfully designed and developed a 3D horror game, utilizing the Godot
	      Engine and Blender for character modeling and environment design.
	\item Conceptualized and crafted a captivating game narrative, character interactions,
	      and immersive horror atmosphere, resulting in a game that received over 10,000 downloads and an overall rating of 4.5/5.
	\item Implemented game mechanics, including player movement, interactions, and
	      enemy AI, resulting in seamless and engaging gameplay
	\item Ensured the game's compatibility with both Windows and Mac platforms,
	      expanding its reach to a broader audience.
\end{itemize}


\noindent
\textbf{Go Santa Go! | 2D Web Game} \hfill December 2021\\
\url{https://quilled.itch.io/go-santa-go} \hfill Godot Engine, HTML, Photo Editing
\begin{itemize}
	\item Utilized the Godot engine to create an engaging and festive 2D game for web platforms.
	\item Achieved 3rd place out of 80 entries in the Jame Gam Christmas Edition competition, with high ratings in gameplay and graphics.
	\item Successfully delivered a fully functional web-based game, reaching a wide audience and showcasing skills in 2D game development.
\end{itemize}

% Experience Section
\section*{EXPERIENCE}

\noindent
\textbf{Toppings} \hfill June 2022 - August 2022\\
\textit{Cashier} \hfill Richmond Hill, Ontario
\begin{itemize}
	\item Assisted customers in a friendly and professional manner, providing exceptional customer service.
	\item Maintained a clean and organized cashier station, ensuring supplies were stocked and readily available.
\end{itemize}

\noindent
\textbf{Sleekkut} \hfill June 2021 - August 2022\\
\textit{Woodworking Assistant} \hfill Richmond Hill, Ontario
\begin{itemize}
	\item Ensured precise measurements, accurate cutting, shaping, and assembly of wood materials.
	\item Utilized woodworking tools, machinery, and techniques to create high-quality, custom-made wood products.
\end{itemize}


\section*{SKILLS}
\begin{itemize}
	\item \textbf{Programming:} Java, Javascript, HTML, CSS, Python, C, GDScript, GLSL, LaTeX, Lua.
	\item \textbf{Tools:} Linux, Git, RESTful API, Vim, OOP, Godot, Blender, Video Editing, Photo Editing.
	\item \textbf{Communication:} Fluent in English and Arabic, with excellent writing and verbal communication skills.
\end{itemize}


\end{document}
