% Document class and font size
\documentclass[a4paper,10pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.8in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Begin document
\begin{document}


% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
	\textbf{\Large ALY TARFA}\\[2pt]
	Richmond Hill, Ontario | \href{mailto:alytarfa@gmail.com}{alytarfa@gmail.com} | (647) 972-2444 | \href{https://www.linkedin.com/in/aly-tarfa-b18b59225/}{Linkedin} | \href{https://alytarfa.me/}{alytarfa.me}
\end{center}

% Education Section
\section*{EDUCATION}
\noindent
\textbf{Carleton University}, Ottawa, Ontario \hfill September 2022 | April 2027\\
Bachelor of Computer Science: Software Engineering Stream, CO-OP \hfill Third Year Standing\\
CGPA: 10.10 (A)

% Experience Section
\section*{EXPERIENCE}

\noindent
\textbf{Toppings} \hfill June 2023 - August 2023\\
\textit{Restaurant Worker} \hfill Richmond Hill, Ontario
\begin{itemize}
	\item Assisted customers in a friendly and professional manner, providing exceptional customer service.
	\item Maintained a clean and organized cashier station, ensuring supplies were stocked and readily available.
    \item Resolved customer complaints and inquiries promptly, enhancing overall customer satisfaction.
    \item Managed the opening and closing procedures of the restaurant.
    \item Handled cash transactions accurately and efficiently, including processing credit/debit card payments
\end{itemize}

\noindent
\textbf{Sleekkut} \hfill June 2021 - August 2022\\
\textit{Social Media and Marketing Manager} \hfill Richmond Hill, Ontario
\begin{itemize}
	\item Monitored social media channels and engaged with the audience to build brand loyalty.
    \item Supported content creation efforts, including writing posts, creating graphics, and producing videos.
    \item Assisted in managing social media advertising campaigns and tracking their performance.
    \item Helped analyze social media data to derive actionable insights for strategy improvement.
\end{itemize}

% Projects Section
\section*{PROJECTS}
\noindent
\textbf{ASCII Art Web App} \hfill November 2023 - January 2024\\
\url{https://github.com/xQuilled/ascii-art-app} \hfill node.js, SQLite, express, CSS, HTML, Javascript
\begin{itemize}
	\item Integrated an external API to enable users to generate text-based ASCII art, adding a unique feature to the website.
	\item Created a reliable database with SQLite3 that enhances the overall performance and security of the website, ensuring smooth user interactions and data integrity.
	\item Implemented user authentication and authorization, allowing users to register and login with a username and password.
	\item Designed a responsive and intuitive user interface, resulting in a seamless user experience.
\end{itemize}


\noindent
\textbf{Within Yourself | 3D Video Game} \hfill December 2021 - January 2022\\
\url{https://quilled.itch.io/within-yourself} \hfill Godot Engine, Blender, GDScript, Audacity
\begin{itemize}
	\item Successfully designed and developed a 3D horror game, utilizing the Godot
	      Engine and Blender for character modeling and environment design.
	\item Conceptualized and crafted a captivating game narrative, character interactions,
	      and immersive horror atmosphere, resulting in a game that received over 10,000 downloads and an overall rating of 4.5/5.
	\item Implemented game mechanics, including player movement, interactions, and
	      enemy AI, resulting in seamless and engaging gameplay
	\item Ensured the game's compatibility with both Windows and Mac platforms,
	      expanding its reach to a broader audience.
\end{itemize}


\section*{SKILLS}
\begin{itemize}
    \item \textbf{Technical} web development, software development, video editing, photo editing, Excel, programming.
	\item \textbf{Communication:} Fluent in English and Arabic, with excellent writing and verbal communication skills.
    Excellent time management and organizational skills \\
    Team collaboration and leadership abilities\\
    Critical thinking and problem-solving skills \\
    Adaptability and ability to learn new technologies quickly
\end{itemize}


\end{document}
